---
title: "Visualization of positive word rates."
author: "Krishna Sreenivas"
date: "September 12, 2017"
output: html_document
---

Below is the visualization for the positive word rate. I have considered the number of positive words per speaker against the total number of positive words.

Following is the code for calculating the positive word rate. This code takes the output file generated by the  python code which has the count of positive words of a speaker.

```
library(jsonlite)

people=c('lehrer','obama','romney')

pos_word_count = c()
for(i in 1:length(people))
  {
  pos_word_count[i] =length(jsonlite::fromJSON(paste(people[i],'.json',sep='')))
  }
```
```{r, warning=FALSE, echo=FALSE}
library(jsonlite)

people=c('lehrer','obama','romney')

pos_word_count = c()
for(i in 1:length(people))
  {
  pos_word_count[i] =length(jsonlite::fromJSON(paste(people[i],'.json',sep='')))
}
```

## Visualization

Following is the visualization for the positive word count.

```{r,echo=FALSE}
barplot(pos_word_count,names.arg=people,col=c('#71BA51','#FF7416','#3D8EB9'),ylim=c(0,200),xlab='Speakers',ylab='Count of positive words',axisnames=TRUE)

```
